---
title: "Google_Project_Cyclistic"
output: html_document
date: '2022-05-12'
---


## Use Cyclistic date to find the differences between the riding pattern of member and casual riders

Data source: https://divvy-tripdata.s3.amazonaws.com/index.html
```{r, warning=FALSE}
library(rmarkdown)
library(ggplot2)
library(tidyverse)
```

### Import and merge data


```{r, warning=FALSE}
data05 <-read.csv("202105-divvy-tripdata.csv")
```
```{r, warning=FALSE}
data06 <-read.csv("202106-divvy-tripdata.csv")
```
```{r, warning=FALSE}
total <- rbind(data05, data06)
head(total)
```
### generate ride_length data
```{r, warning=FALSE}
total$ride_length <- as.POSIXct(total$ended_at) - as.POSIXct(total$started_at)
```
```{r, warning=FALSE}
member <- data.frame(filter(total, total$member_casual == 'member'))
casual <- data.frame(filter(total, total$member_casual == 'casual'))
```



### Calculate mean for member and casual group
```{r, warning=FALSE}
member_mean = mean(member$ride_length)
casual_mean = mean(casual$ride_length)
member_mean
casual_mean
```

### Vizualization for the mean
```{r, warning=FALSE}
dat <- data.frame(x=c(member_mean,casual_mean),y=c("member","casual"))
```


```{r, warning=FALSE}
dat
```


```{r, warning=FALSE}
ggplot(data = dat, aes(x= y,y = x))+ geom_col()+
  labs(x ="type", y= "Avg_ride_time")
```
### From the plot, Casual riders tend to ride longer each time than members 

### Next, Check the relationship between weekday and lengths of ride

```{r, warning=FALSE}
typeof(total$started_at)
```

```{r, warning=FALSE}
total$isweekdays <-weekdays(as.Date(total$started_at))
```


```{r, warning=FALSE}
typeof(total$isweekdays)
```


```{r, warning=FALSE}
member <- data.frame(filter(total, total$member_casual == "member"))
casual <- data.frame(filter(total, total$member_casual == "casual"))

mean_member_week = group_by(member, isweekdays)%>%
  summarise_each(funs(mean))
mean_casual_week = group_by(casual, isweekdays)%>%
  summarise_each(funs(mean))
```
```{r, warning=FALSE}
mean_member_week
mean_casual_week
```
### Creat vizualization
```{r, warning=FALSE}
mean_of_week <- rbind(mean_casual_week, mean_member_week)
```
```{r, warning=FALSE}
ggplot(data = mean_casual_week, aes(x= isweekdays,y = ride_length))+ geom_col()+
  labs( y= "Avg_ride_time_for casual")
ggplot(data = mean_member_week, aes(x= isweekdays,y = ride_length))+ geom_col()+
  labs( y= "Avg_ride_time_for member")
```
## plot shows that weekdays doesn't significantly effect the avg ride length

```{r, warning=FALSE}
ggplot(data = member, aes(x= isweekdays))+ geom_bar()
ggplot(data = casual, aes(x= isweekdays))+ geom_bar()  


```

### for members, they ride averagely.While, casual riders ride much more frequent in weekends.

